Forecasting the old-age dependency ratio to determine the best pension age

### 2020-08-24 PensionAge.Rmd
Added renv lock, updated all packages and recompiled

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
library(tidyverse)
library(demography)
# remotes::install_github("robjhyndman/addb")
library(addb)
library(patchwork)
library(kableExtra)
source("functions-v4.R")
```

@@

# Get fertility data for 1921-2006
aus.fert <- aus.fertility
births <- aus.fert$rate$female * aus.fert$pop$female
# Get latest fertility data from ABS (downloaded 30 April 2020)
ausf <- readr::read_csv("FERTILITY_AGE_STATE_30042020143630412.csv") %>%
  filter(
    Region == "Australia",
    Age %in% paste(15:49),
  ) %>%
  mutate(
    Year = Time,
    Age = as.numeric(Age)
  ) %>%
  select(Year, Age, Measure, Value)
# Extract births and population values
newbirths <- ausf %>%
  filter(Measure == "Births") %>%
  mutate(Value = Value * 1000) %>%
  select(-Measure) %>%
  pivot_wider(names_from = Year, values_from = Value) %>%
  select(-Age) %>%
  as.matrix()
newpop <- ausf %>%
  filter(Measure == "Female population") %>%
  mutate(Value = Value) %>%
  select(-Measure) %>%
  pivot_wider(names_from = Year, values_from = Value) %>%
  select(-Age) %>%
  as.matrix()
rownames(newbirths) <- rownames(newpop) <- 15:49

@@

```{r pensionagetables2, dependson="OADRat65", message=FALSE}
pension_age_optimal %>%
  mutate(
    MonthLo = round((Lo80 - trunc(Lo80)) * 12),
    MonthHi = round((Hi80 - trunc(Hi80)) * 12),
    AgeLo = paste0(
      trunc(Lo80), "Y",
      if_else(MonthLo > 0, paste0("+", MonthLo, "M"), "")
    ),
    AgeHi = paste0(
      trunc(Hi80), "Y",
      if_else(MonthHi > 0, paste0("+", MonthHi, "M"), "")
    ),
    Column = trunc((Year - 2019) / 10) + 1,
  ) %>%
  select(Year, AgeLo, AgeHi, Column) %>%
  nest(data = c(Year = Year, Lo = AgeLo, Hi = AgeHi)) %>%
  pivot_wider(names_from = Column, values_from = data) %>%
  unnest(cols = paste(1:5), names_repair = "unique") %>%
  knitr::kable(
    format = "latex",
    col.names = rep(c("Year", "Lo", "Hi"), 5),
    booktabs = TRUE,
    caption = "Fifty-year lower and higher boundary of pension age scheme with 80\\% confidence. Y denotes years and M denotes months."
  ) %>%
  kable_styling(font_size = 7)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
library(dplyr)
library(tidyr)
library(ggplot2)
library(demography)
library(patchwork)
source("functions-v4.R")
```

@@

# Get fertility data for 1921-2006
aus.fert <- addb::aus.fertility
births <- aus.fert$rate$female * aus.fert$pop$female
# Get latest fertility data from ABS (downloaded 30 April 2020)
ausf <- readr::read_csv("FERTILITY_AGE_STATE_30042020143630412.csv") %>%
  filter(
    Region == "Australia",
    Age %in% paste(15:49),
  ) %>%
  mutate(
    Year = Time,
    Age = as.numeric(Age)
  ) %>%
  select(Year, Age, Measure, Value)
# Extract births and population values
newbirths <- ausf %>%
  filter(Measure == "Births") %>%
  mutate(Value = Value * 1000) %>%
  select(-Measure) %>%
  pivot_wider(names_from = Year, values_from = Value) %>%
  select(-Age) %>%
  as.matrix()
newpop <- ausf %>%
  filter(Measure == "Female population") %>%
  mutate(Value = Value) %>%
  select(-Measure) %>%
  pivot_wider(names_from = Year, values_from = Value) %>%
  select(-Age) %>%
  as.matrix()
rownames(newbirths) <- rownames(newpop) <- 15:49

@@

```{r pensionagetables2, dependson="OADRat65", message=FALSE}
pension_age_optimal %>%
  mutate(
    MonthLo = round((Lo80 - trunc(Lo80)) * 12),
    MonthHi = round((Hi80 - trunc(Hi80)) * 12),
    AgeLo = paste0(
      trunc(Lo80), "Y",
      if_else(MonthLo > 0, paste0("+", MonthLo, "M"), "")
    ),
    AgeHi = paste0(
      trunc(Hi80), "Y",
      if_else(MonthHi > 0, paste0("+", MonthHi, "M"), "")
    ),
    Column = trunc((Year - 2019) / 10) + 1,
  ) %>%
  select(Year, AgeLo, AgeHi, Column) %>%
  nest(data = c(Year = Year, Lo = AgeLo, Hi = AgeHi)) %>%
  pivot_wider(names_from = Column, values_from = data) %>%
  unnest(cols = paste(1:5), names_repair = "unique") %>%
  knitr::kable(
    format = "latex",
    col.names = rep(c("Year", "Lo", "Hi"), 5),
    booktabs = TRUE,
    caption = "Fifty-year lower and higher boundary of pension age scheme with 80\\% confidence. Y denotes years and M denotes months."
  ) %>%
  kableExtra::kable_styling(font_size = 7)
```

@@

\newpage

### Colophon {-}

This report was generated on `r Sys.time()`.

The current Git commit details are:

```{r}
## Which commit is this file at?
git2r::repository(here::here())
```

We used the following computational environment and dependencies:

```{r colophon, cache=FALSE}
options(width=100)
## Which R packages and versions?
devtools::session_info()
```

\newpage

### 2020-08-24 PensionAge.tex
Added renv lock, updated all packages and recompiled

>>>>

\newpage

\hypertarget{colophon}{%
\subsubsection*{Colophon}\label{colophon}}
\addcontentsline{toc}{subsubsection}{Colophon}

This report was generated on 2020-08-24 15:26:49.

The current Git commit details are:

\begin{verbatim}
## Local:    master /home/robjhyndman/git/Research/PensionAge
## Remote:   master @ origin (git@github.com:robjhyndman/PensionAge.git)
## Head:     [e16a85d] 2020-05-05: [ImgBot] Optimize images
\end{verbatim}

We used the following computational environment and dependencies:

\begin{verbatim}
## - Session info -----------------------------------------------------------------------------------
##  setting  value                       
##  version  R version 4.0.2 (2020-06-22)
##  os       Ubuntu 20.04.1 LTS          
##  system   x86_64, linux-gnu           
##  ui       X11                         
##  language en_AU:en                    
##  collate  en_AU.UTF-8                 
##  ctype    en_AU.UTF-8                 
##  tz       Australia/Melbourne         
##  date     2020-08-24                  
## 
## - Packages ---------------------------------------------------------------------------------------
##  ! package            * version  date       lib source                                         
##  P abind                1.4-5    2016-07-21 [?] CRAN (R 4.0.0)                                 
##  P assertthat           0.2.1    2019-03-21 [?] CRAN (R 4.0.0)                                 
##  P backports            1.1.6    2020-04-05 [?] CRAN (R 4.0.0)                                 
##    bookdown             0.18     2020-03-05 [1] CRAN (R 4.0.0)                                 
##  P callr                3.4.3    2020-03-28 [?] CRAN (R 4.0.0)                                 
##  P cli                  2.0.2    2020-02-28 [?] CRAN (R 4.0.0)                                 
##  P cluster              2.1.0    2019-06-19 [?] CRAN (R 4.0.0)                                 
##  P cobs                 1.3-4    2020-01-24 [?] CRAN (R 4.0.0)                                 
##    codetools            0.2-16   2018-12-24 [1] CRAN (R 4.0.0)                                 
##  P colorspace           1.4-1    2019-03-18 [?] CRAN (R 4.0.0)                                 
##  P crayon               1.3.4    2017-09-16 [?] CRAN (R 4.0.0)                                 
##  P curl                 4.3      2019-12-02 [?] CRAN (R 4.0.0)                                 
##  P demography         * 1.22     2019-04-22 [?] CRAN (R 4.0.0)                                 
##  P desc                 1.2.0    2018-05-01 [?] CRAN (R 4.0.0)                                 
##    devtools             2.3.0    2020-04-10 [1] CRAN (R 4.0.0)                                 
##  P digest               0.6.25   2020-02-23 [?] CRAN (R 4.0.0)                                 
##  P dplyr              * 0.8.5    2020-03-07 [?] CRAN (R 4.0.0)                                 
##  P ellipsis             0.3.0    2019-09-20 [?] CRAN (R 4.0.0)                                 
##  P evaluate             0.14     2019-05-28 [?] CRAN (R 4.0.0)                                 
##  P fansi                0.4.1    2020-01-08 [?] CRAN (R 4.0.0)                                 
##  P farver               2.0.3    2020-01-16 [?] CRAN (R 4.0.0)                                 
##  P fda                  5.1.4    2020-04-20 [?] CRAN (R 4.0.0)                                 
##  P forecast           * 8.12     2020-03-31 [?] CRAN (R 4.0.0)                                 
##  P fracdiff             1.5-1    2020-01-24 [?] CRAN (R 4.0.0)                                 
##  P fs                   1.4.1    2020-04-04 [?] CRAN (R 4.0.0)                                 
##  P ftsa                 5.6      2020-04-23 [?] CRAN (R 4.0.0)                                 
##  P geometry             0.4.5    2019-12-04 [?] CRAN (R 4.0.0)                                 
##  P ggplot2            * 3.3.0    2020-03-05 [?] CRAN (R 4.0.0)                                 
##  P git2r                0.27.1   2020-05-03 [?] CRAN (R 4.0.0)                                 
##  P glue                 1.4.0    2020-04-03 [?] CRAN (R 4.0.0)                                 
##  P gtable               0.3.0    2019-03-25 [?] CRAN (R 4.0.0)                                 
##  P hdrcde               3.3      2018-12-21 [?] CRAN (R 4.0.0)                                 
##    here                 0.1      2017-05-28 [1] CRAN (R 4.0.0)                                 
##  P highr                0.8      2019-03-20 [?] CRAN (R 4.0.0)                                 
##  P hms                  0.5.3    2020-01-08 [?] CRAN (R 4.0.0)                                 
##  P htmltools            0.4.0    2019-10-04 [?] CRAN (R 4.0.0)                                 
##  P httr                 1.4.1    2019-08-05 [?] CRAN (R 4.0.0)                                 
##  P kableExtra           1.1.0    2019-03-16 [?] CRAN (R 4.0.0)                                 
##  P KernSmooth           2.23-17  2020-04-26 [?] CRAN (R 4.0.0)                                 
##  P knitr                1.28     2020-02-06 [?] CRAN (R 4.0.0)                                 
##  P ks                   1.11.7   2020-02-11 [?] CRAN (R 4.0.0)                                 
##  P labeling             0.3      2014-08-23 [?] CRAN (R 4.0.0)                                 
##  P latex2exp          * 0.4.0    2015-11-30 [?] CRAN (R 4.0.0)                                 
##  P lattice              0.20-41  2020-04-02 [?] RSPM (R 4.0.0)                                 
##  P lifecycle            0.2.0    2020-03-06 [?] CRAN (R 4.0.0)                                 
##  P lmtest               0.9-37   2019-04-30 [?] CRAN (R 4.0.0)                                 
##  P magic                1.5-9    2018-09-17 [?] CRAN (R 4.0.0)                                 
##  P magrittr             1.5      2014-11-22 [?] CRAN (R 4.0.0)                                 
##  P MASS                 7.3-51.6 2020-04-26 [?] CRAN (R 4.0.0)                                 
##  P Matrix               1.2-18   2019-11-27 [?] CRAN (R 4.0.0)                                 
##  P MatrixModels         0.4-1    2015-08-22 [?] CRAN (R 4.0.0)                                 
##  P mclust               5.4.6    2020-04-11 [?] CRAN (R 4.0.0)                                 
##    memoise              1.1.0    2017-04-21 [1] CRAN (R 4.0.0)                                 
##  P mgcv                 1.8-31   2019-11-09 [?] CRAN (R 4.0.0)                                 
##    MonashEBSTemplates   0.2      2020-05-04 [1] Github (robjhyndman/MonashEBSTemplates@dc32000)
##  P munsell              0.5.0    2018-06-12 [?] CRAN (R 4.0.0)                                 
##  P mvtnorm              1.1-0    2020-02-24 [?] RSPM (R 4.0.0)                                 
##  P nlme                 3.1-147  2020-04-13 [?] RSPM (R 4.0.0)                                 
##  P nnet                 7.3-14   2020-04-26 [?] CRAN (R 4.0.0)                                 
##  P patchwork          * 1.0.0    2019-12-01 [?] CRAN (R 4.0.0)                                 
##  P pcaPP                1.9-73   2018-01-14 [?] CRAN (R 4.0.0)                                 
##  P pdfCluster           1.0-3    2018-12-04 [?] CRAN (R 4.0.0)                                 
##  P pillar               1.4.3    2019-12-20 [?] CRAN (R 4.0.0)                                 
##  P pkgbuild             1.0.7    2020-04-25 [?] CRAN (R 4.0.0)                                 
##  P pkgconfig            2.0.3    2019-09-22 [?] CRAN (R 4.0.0)                                 
##  P pkgload              1.0.2    2018-10-29 [?] CRAN (R 4.0.0)                                 
##  P prettyunits          1.1.1    2020-01-24 [?] CRAN (R 4.0.0)                                 
##  P processx             3.4.2    2020-02-09 [?] CRAN (R 4.0.0)                                 
##  P ps                   1.3.2    2020-02-13 [?] CRAN (R 4.0.0)                                 
##  P purrr                0.3.4    2020-04-17 [?] RSPM (R 4.0.0)                                 
##  P quadprog             1.5-8    2019-11-20 [?] CRAN (R 4.0.0)                                 
##  P quantmod             0.4.17   2020-03-31 [?] CRAN (R 4.0.0)                                 
##  P quantreg             5.55     2020-04-01 [?] CRAN (R 4.0.0)                                 
##  P R6                   2.4.1    2019-11-12 [?] CRAN (R 4.0.0)                                 
##  P rainbow              3.6      2019-01-29 [?] CRAN (R 4.0.0)                                 
##  P RColorBrewer         1.1-2    2014-12-07 [?] CRAN (R 4.0.0)                                 
##  P Rcpp                 1.0.4.6  2020-04-09 [?] CRAN (R 4.0.0)                                 
##  P readr                1.3.1    2018-12-21 [?] CRAN (R 4.0.0)                                 
##  P remotes              2.1.1    2020-02-15 [?] CRAN (R 4.0.0)                                 
##    renv                 0.9.3    2020-02-10 [1] CRAN (R 4.0.0)                                 
##    rlang                0.4.6    2020-05-02 [1] CRAN (R 4.0.0)                                 
##  P rmarkdown            2.1      2020-01-20 [?] CRAN (R 4.0.0)                                 
##  P rprojroot            1.3-2    2018-01-03 [?] CRAN (R 4.0.0)                                 
##  P rstudioapi           0.11     2020-02-07 [?] CRAN (R 4.0.0)                                 
##  P rvest                0.3.5    2019-11-08 [?] CRAN (R 4.0.0)                                 
##  P scales               1.1.0    2019-11-18 [?] CRAN (R 4.0.0)                                 
##  P sde                  2.0.15   2016-04-13 [?] CRAN (R 4.0.0)                                 
##    sessioninfo          1.1.1    2018-11-05 [1] CRAN (R 4.0.0)                                 
##  P SparseM              1.78     2019-12-13 [?] RSPM (R 4.0.0)                                 
##  P stringi              1.4.6    2020-02-17 [?] CRAN (R 4.0.0)                                 
##  P stringr              1.4.0    2019-02-10 [?] CRAN (R 4.0.0)                                 
##  P testthat             2.3.2    2020-03-02 [?] CRAN (R 4.0.0)                                 
##  P tibble               3.0.1    2020-04-20 [?] CRAN (R 4.0.0)                                 
##  P tidyr              * 1.0.2    2020-01-24 [?] CRAN (R 4.0.0)                                 
##  P tidyselect           1.0.0    2020-01-27 [?] CRAN (R 4.0.0)                                 
##  P timeDate             3043.102 2018-02-21 [?] CRAN (R 4.0.0)                                 
##  P tseries              0.10-47  2019-06-05 [?] CRAN (R 4.0.0)                                 
##  P TTR                  0.23-6   2019-12-15 [?] CRAN (R 4.0.0)                                 
##  P urca                 1.3-0    2016-09-06 [?] CRAN (R 4.0.0)                                 
##    usethis              1.6.1    2020-04-29 [1] CRAN (R 4.0.0)                                 
##  P vctrs                0.2.4    2020-03-10 [?] CRAN (R 4.0.0)                                 
##  P viridisLite          0.3.0    2018-02-01 [?] CRAN (R 4.0.0)                                 
##  P webshot              0.5.2    2019-11-22 [?] CRAN (R 4.0.0)                                 
##  P withr                2.2.0    2020-04-20 [?] CRAN (R 4.0.0)                                 
##  P xfun                 0.13     2020-04-13 [?] CRAN (R 4.0.0)                                 
##  P xml2                 1.3.2    2020-04-23 [?] CRAN (R 4.0.0)                                 
##  P xts                  0.12-0   2020-01-19 [?] CRAN (R 4.0.0)                                 
##  P yaml                 2.2.1    2020-02-01 [?] CRAN (R 4.0.0)                                 
##  P zoo                  1.8-7    2020-01-10 [?] CRAN (R 4.0.0)                                 
## 
## [1] /home/robjhyndman/git/Research/PensionAge/renv/library/R-4.0/x86_64-pc-linux-gnu
## [2] /tmp/RtmpYSnVGN/renv-system-library
## 
##  P -- Loaded and on-disk path mismatch.
\end{verbatim}

\newpage
